---
title: "vignette"
author: "Zuxiang Li, Ying Luo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(assignment4Package)
```

# Linreg Reference Class Object
Linreg class requires two arguments: formula and data, and it calculate Regressions coefficient, fitted values, residuals, degrees of freedom, and residual variance of multiple regression model.

## print()
This function should print out the coefficients and coefficient names, similar as done by the lm class.
```{r}
data(iris)
l1<-linreg$new(Petal.Length~Species, data=iris)

l1$print()
```

## plot()

```{r}
data(iris)
l1<-linreg$new(Petal.Length~Species, data=iris)

l1$plot()
```

## resid()
This function should return the vector of residuals.

```{r}
data(iris)
l1<-linreg$new(Petal.Length~Species, data=iris)

l1$resid()
```

## pred()
This function should return the predicted values.

```{r}
data(iris)
l1<-linreg$new(Petal.Length~Species, data=iris)

l1$pred()
```

## coef()
This function should return the coefficients as a named vector.

```{r}
data(iris)
l1<-linreg$new(Petal.Length~Species, data=iris)

l1$coef()
```

## summary()
This function should return a similar printout as printed for lm objects, but you only need to present the coefficients with their standard error, t-value and p-value as well as the estimate of σˆ and the degrees of freedom in the model.

```{r}
data(iris)
l1<-linreg$new(Petal.Length~Species, data=iris)

l1$summary()
```

# * Linreg_qr Reference Class Object
Linreg_qr class has the same function with Linreg class, but using QR Decomposition.

